%-------------------------
% Resume in Latex
% Author : Omkar Pote
% Based off of: https://github.com/jakegut/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\vspace*{30pt} \Huge \scshape Omkar Pote} \\ \vspace{5pt} 
    % 123 Street Name, Town, State 12345 \\ \vspace{1pt}
    \small
    \href{https://omkarpote.com}{\raisebox{-0.2\height}\faGlobe\  \underline{omkarpote.com}} ~ 
    \href{mailto:omkrpt@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{omkrpt@gmail.com}} ~
    \href{https://github.com/omkrpt}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/omkrpt}} ~ 
    \href{https://linkedin.com/in/omkrpt/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/omkrpt}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Purdue University}{August 2024 -- Present}
      {\textbf{Master of Science in Computer and Information Technology}}{4.0/4.0}
      \vspace{-8pt}
      \resumeSubSubheading
      {Research Focus: Data Management for Machine Learning Pipelines}{}
      \vspace{-18pt}
      \resumeSubSubheading
      {Graduate Coursework: AI, Data Mining, Responsible Data Science, Natural Language Technologies}{}  
      \vspace{-8pt}
    \resumeSubheading
      {Indian Institute of Technology, Madras}{July 2016 -- May 2020}
      {\textbf{Bachelor of Technology}}{}
  \resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI/ML:}{ Explainable AI (XAI), Algorithmic Fairness, Causal Inference, Counterfactual Explanations, Data Distribution Shift, Tabular Data Modeling, Time Series Classification, Dimensionality Reduction, NLP} \\
     \textbf{Data Engineering:}{ Data Cleaning, ETL, Spark, Databricks, Hadoop, MySQL, MongoDB, Neo4j} \\
     \textbf{Languages:}{ Python, Java, C/C++, Scala, Bash, SQL, LaTeX} \\
     \textbf{ML Frameworks:}{ Scikit-learn, TensorFlow, PyTorch, Keras} \\
     \textbf{Software Development:}{ OOP, SOLID, System Design, Microservices, Spring Boot, REST APIs, CI/CD, Git, Agile} \\
     \textbf{Cloud \& Containers:}{ AWS(EC2, EMR, S3), DigitalOcean, Docker, Kubernetes} \\
     \textbf{Tools/Frameworks:}{ MATLAB, Simulink, OpenMP, RabbitMQ, Redis, NodeJS, ReactJS} \\
    }}

 \end{itemize}
 \vspace{-16pt}


%-----------Research Experience-----------
\section{Research Experience}
\vspace{4pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Purdue University}{Aug 2024 -- Present}
      {Graduate Research Assistant (Part-Time)}{}
      \resumeItemListStart
        \resumeItem{Working in the 
        \href{https://romilapradhan.github.io/}{\underline{Responsible Data Science Lab}} under Dr. Romila Pradhan.
        }
        \resumeItem{ Current research focus area: Data Management for Machine Learning Pipelines. 
        }
      \resumeItemListEnd
    \resumeSubheading
      {IIT Madras}{Oct 2023 -- Jun 2024}
      {Project Scientist, iACE Lab}{}
      \resumeItemListStart
        \resumeItem{Worked in the American Express Lab for Data Analytics, Risk \& Technology
        \href{https://dart.iitm.ac.in/}{\underline{(DART)}}
        / Intelligent Applications in Chemical Engineering
        \href{https://home.iitm.ac.in/raj/}{\underline{(iACE)}}
        Lab under \href{https://scholar.google.co.in/citations?user=LItoQlMAAAAJ&hl=en}{\underline{Dr. Rajagopalan Srinivasan}}.
        }
        \resumeItem{ Focused on Explainable AI methods for Fault Detection and Diagnosis in Process Monitoring Systems. 
        }
        \resumeItem{ Increased the reliability and trustworthiness of black-box AI systems by developing model-agnostic, counterfactual-based explainability techniques for multivariate time series classification.
        }
      \resumeItemListEnd

\vspace{-8pt}

%-----------Academic Service-----------
\section{Academic Service}
    \resumeItemListStart
    \resumeItem{
        External Reviewer, IEEE International Conference on Data Engineering 
        \href{https://ieee-icde.org/2025/}{\underline{(ICDE)}} 2025.
    }
    \resumeItem{
        External Reviewer, International Conference on Extending Database Technology
        \href{https://edbticdt2026.github.io/}{\underline{(EDBT)}} 2026.
    }
    \resumeItemListEnd
\vspace{-8pt}

%-----------Professional Experience-----------
\section{Professional Experience}
    \resumeSubheading
      {IIT Madras}{Oct 2023 -- Jun 2024}
      {Software Quality Mentor, HILCPS Lab}{}
      \resumeItemListStart
        \resumeItem{Worked with the Human-in-the-Loop Cyber-Physical Systems 
        \href{https://home.iitm.ac.in/babji.srinivasan/index.html}{\underline{(HILCPS)}}
         Lab, led by Dr. Babji Srinivasan.
        }
        \resumeItem{Led architecture, planning, and cloud migration for an IoT project using Flutter, Django, and Embedded C, while ensuring enterprise-level best practices.
        }
        \resumeItem{Conducted code reviews, refactoring, and fortnightly sessions on agile methodologies, version control, code hygiene, unit testing, and design patterns.
        }
    \resumeItemListEnd

\pagebreak \vspace*{0pt}
    
    \resumeSubheading
      {Capillary Technologies}{May 2020 -- Sep 2023}
      {Software Development Engineer, Payments}{Dec 2021 -- Sep 2023}
      \resumeItemListStart
        \resumeItem{
        Led the design and implementation of POTATO, a robust microservice-based solution enabling seamless, cashless fuel transactions, with secure APIs for payment providers, fuel stations, and third-party services.
        }
        \resumeItem{
        Built and optimized the system using Spring Boot, MySQL, MongoDB, and RabbitMQ, handling 10,000+ transactions per minute, while also establishing CI/CD pipelines and real-time monitoring for performance.
        }
      \resumeItemListEnd

    \resumeSubSubheading
      {Big Data Engineer, Extract-Transform-Load (ETL)}{Oct 2020 -- Nov 2021}
      \resumeItemListStart
        \resumeItem{Managed Capillary’s in-house data warehousing and ETL system for its flagship CRM and BI product, processing 6+ billion daily records into a star schema model with facts, dimensions, and KPIs.}
        \resumeItem{Developed REST APIs for data transfer between microservices and optimized real-time Spark queries on AWS EMR clusters.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Intern}{May 2020 -- Sep 2020}
      \resumeItemListStart
        \resumeItem{Built internal developer tools to handle the ETL process. This includes GUIs for end-to-end control and monitoring of executions from Neo4j, where the queries are stored as a Directed Acyclic Graph.}
      \resumeItemListEnd


    \resumeSubheading
      {Tesco}{May 2019 -- Jul 2019}
      {Software Engineering Intern}{}
      \resumeItemListStart
        \resumeItem{Automated Tesco's food donation system by eliminating a labor-intensive step in stock management, optimizing processes for 2500+ stores and 6000+ charities.
        }
        \resumeItem{Developed a Donation Assistant API for product classification, implemented an Apache Nifi and Python Flask-based pipeline, reducing administrative workload by 20\%, and enhanced donation accuracy/relevance by over 15\% through data analysis using R tidyverse package.
        }
    \resumeItemListEnd

    \resumeSubheading
      {Crest IT Consulting}{Jun 2018 -- Jul 2018}
      {Web Development Intern}{}
      \resumeItemListStart
        \resumeItem{Took up a complete rebranding initiative for the company, involving the development of a new website, logo, and brand identity. Check out \href{https://crestit.in}{\underline{crestit.in}}.
        }
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Activities and Projects}
    \resumeSubHeadingListStart
        \resumeSubSubheading
            {Projects}{}
            \resumeItemListStart
                \resumeItem{\textbf{Yuj (formerly Caval):} Contributed as a founding team member for this IITM-based startup, which provided doorstep vehicle repair services. Led the development of the entire branding, logo, website, app, and other marketing materials.}
                \resumeItem{\textbf{ChemClave:} Created the ChemClave 2017 website as part of the WebOps team, for the annual event organised by the Chemical Engineering Society (CheS) of IIT Madras.}
                \resumeItem{\textbf{Cuckoo Dooku:} Developed a Star Wars-themed, open-source Chrome extension for productivity. Received a commendation in the FOSS hackathon 2021. See \href{https://github.com/omkrpt/cuckoo-dooku}{\underline{github.com/omkrpt/cuckoo-dooku}}}
                \resumeItem{\textbf{Snake Game:} Coded the game from scratch as a high school project. See
                \href{https://omkarpote.com/\#snake}{\underline{omkarpote.com/\#snake}}}
            \resumeItemListEnd
        \resumeSubSubheading
            {Graphic Design}{}
            \resumeItemListStart
                \resumeItem{\textbf{Technical Proficiency:} Skilled in graphic design using the Adobe Suite including Photoshop, Illustrator, Premiere Pro, and Indesign}
                \resumeItem{\textbf{Freelance Experience:} Freelanced for various clients from Dec'16 to Aug'18. Portfolio at 
                \href{https://www.behance.net/omkarpote}{\underline{behance.net/omkarpote}}}
                \resumeItem{\textbf{Head of Design, Entrepreneurship Cell, IIT Madras:} Led a team of 16 designers and associate designers, developing creative content for digital and printed media, over two semesters.}
                \resumeItem{\textbf{Inter IIT Sports Meet:} As part of the organizing team of the 2017 edition, designed marketing content, venue setups, and ambience for the tournament.}
            \resumeItemListEnd
        \resumeSubSubheading
            {Extracurriculars}{}
            \resumeItemListStart
                \resumeItem{\textbf{Department Soccer Team Captain:} Led the Chemical Engineering department soccer team to a third-place finish in the IITM Inter Department League 2018-19.}
                \resumeItem{\textbf{Karate:} Black belt holder with numerous accolades and medals on the national level, showcasing over 11 years of dedicated practice.}
                \resumeItem{\textbf{Music Certification:} Cleared ABGMVM's Hindustani Classical Music Exam with a score of 45/50.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd

References are available upon request.
    

\end{document}
